
---
title: "2022 Rating Curves"
author: "Jake Cavaiani, Karen Jorgenson"
date: "11/7/2022"
output:
  html_document:
    df_print: paged
  pdf_document: default
  word_document: default
---
The purpose of this script is to read in pressure transducer data from 2022 and generate rating curves to ultimately generate predicted continuous discharge records throughout the whole season.

Read in most updated merged files from each site from the google drive (DoD Project->2022 AK sensors->Discharge->site->"merged_date_file" )


```{r setup, include = FALSE}
# Load packages #
library(tidyverse)
library(lubridate)
library(data.table)
library(rio)
library(ggplot2)
library(scales)
library(psych)
library(here)
library(googledrive)
library(readxl)
library(cowplot)
library(zoo)
library(readr)
library(dplyr)
library(RColorBrewer)
library(gridExtra)
library(ggpmisc)
library(birk)
library(imputeTS)
```



### ALL Sites ###

```{r, warning = FALSE, message = FALSE}
# Import data from google drive #
discharge.2022 <- "https://docs.google.com/spreadsheets/d/e/2PACX-1vQR6HHHDpnxc6DmNHfdNLR9-dgDHR5Imt0Ve4_t2DzIF18_8D3O2da5zcWQzJUSoFQfaetPZDeXZ610/pub?gid=0&single=true&output=csv"
QSummary.2022 <- read.csv(url(discharge.2022))

### Format Time ###
QSummary.2022$Date <- mdy(QSummary.2022$Date)
QSummary.2022$DateTimeAK <- as.POSIXct(paste(QSummary.2022$Date, QSummary.2022$Time), format = "%Y-%m-%d %H:%M", tz = "America/Anchorage")
QSummary.2022$DateTimeAK <- lubridate::round_date(QSummary.2022$DateTimeAK, "60 minutes")

### ALL Sites ###
QSummary.2022 %>% ggplot() +
  geom_point(aes(x=DateTimeAK, y=MeasuredQ_Ls, color=Site, shape=Method), size=3) +
  theme_classic() +
  scale_color_manual(values=c("#FF7F00","#A6761D", "#6A3D9A", "#66C2A5", "#E7298A")) + ggtitle("ALL SITES") 



```

Here is all the discrete discharge measurements for 2022

Eielson atmospheric pressure data will be used to fill gaps in air pressure.
```{r, warning = FALSE, message = FALSE}
eielson.atmo.2022.url <- "https://docs.google.com/spreadsheets/d/e/2PACX-1vQjJbkVdOseFUsTFMDXaHRoKkPiFt6Uvc-9R3tkFZxKFjqSmPPgZzexdbhezBr_qYgGUdVN6ywYR28c/pub?output=csv"

eielson.atmo.2022 <- read.csv(url(eielson.atmo.2022.url), skip = 6) 
eielson.atmo.2022 <- eielson.atmo.2022[-1,]

names(eielson.atmo.2022) <- c("Site", "DateTimeAK", "sea_level_pressure", "AirPressure")

eielson.atmo.2022$DateTimeAK <- mdy_hm(eielson.atmo.2022$DateTimeAK)

# Correct time zone
eielson.atmo.2022$DateTimeAK <- eielson.atmo.2022$DateTimeAK - 28800
eielson.atmo.2022$DateTimeAK <- force_tz(eielson.atmo.2022$DateTimeAK, tzone = "America/Anchorage")
#attributes(eielson.atmo.2022$DateTimeAK)$tzone <- "America/Anchorage"

eielson.atmo.2022$DateTimeAK <- lubridate::round_date(eielson.atmo.2022$DateTimeAK, "15 minutes")

eielson.atmo.2022$AirPressure <- as.numeric(eielson.atmo.2022$AirPressure)
eielson.atmo.2022$sea_level_pressure <- as.numeric(eielson.atmo.2022$sea_level_pressure)

# Take average at 15 min interval
eielson.atmo.2022 <- eielson.atmo.2022 %>% group_by(DateTimeAK) %>% summarise(DateTimeAK = unique(DateTimeAK), AirPressure = mean(AirPressure),
      sea_level_pressure = mean(sea_level_pressure))


eielson.atmo.2022$AirPressure <- eielson.atmo.2022$AirPressure*3.38639 # converting from inHG to kPa

## conversion to elevation at each site
# MOOS elevation is 574 feet
# POKE 760.96 ft
# STRT 820 ft
# FRCH 601 ft 
# VAUL 688.8 ft

eielson.atmo.2022.compare <- eielson.atmo.2022
eielson.atmo.2022.compare$mmHG <- eielson.atmo.2022.compare$sea_level_pressure * 25.44 # converting to mmHG

 
# MOOS 
eielson.atmo.2022.compare$mmHGcorrectedMOOS <- eielson.atmo.2022.compare$mmHG - (2.5*574/100) 
eielson.atmo.2022.compare$AirPressureCorrectedMOOS <- eielson.atmo.2022.compare$mmHGcorrectedMOOS * 0.133322 # converting this to kPA to compare with MOOS PT

# POKE 
eielson.atmo.2022.compare$mmHGcorrectedPOKE <- eielson.atmo.2022.compare$mmHG - (2.5*760.96/100) 
eielson.atmo.2022.compare$AirPressureCorrectedPOKE <- eielson.atmo.2022.compare$mmHGcorrectedPOKE * 0.133322 # converting this to kPA 

# STRT
eielson.atmo.2022.compare$mmHGcorrectedSTRT <- eielson.atmo.2022.compare$mmHG - (2.5*820/100) 
eielson.atmo.2022.compare$AirPressureCorrectedSTRT <- eielson.atmo.2022.compare$mmHGcorrectedSTRT * 0.133322 # converting this to kPA 

# FRCH
eielson.atmo.2022.compare$mmHGcorrectedFRCH <- eielson.atmo.2022.compare$mmHG - (2.5*601/100) 
eielson.atmo.2022.compare$AirPressureCorrectedFRCH <- eielson.atmo.2022.compare$mmHGcorrectedFRCH * 0.133322 # converting this to kPA 

# VAUL
eielson.atmo.2022.compare$mmHGcorrectedVAUL <- eielson.atmo.2022.compare$mmHG - (2.5*688.8/100)
eielson.atmo.2022.compare$AirPressureCorrectedVAUL <- eielson.atmo.2022.compare$mmHGcorrectedVAUL * 0.133322 # converting this to kPA 
```

### MOOS #### 
```{r, warning = FALSE, message = FALSE}
# Load in water pressure data 
# urls
moos.atmo.2022.url <- "https://docs.google.com/spreadsheets/d/e/2PACX-1vQ7QMNWjVX1R43qflIW7lVqkj7wRHouhgQhWK76kfR8zK-UZg9bFSm92ccPy8T0luhFHKwsLNQQjA56/pub?output=csv"
moos.stream.one.2022.url <- "https://docs.google.com/spreadsheets/d/e/2PACX-1vRo04g32Yr3DsZbXQiw6VTPfgWuWq5csh1VhxfMy3IT3U6OkJOGvTlofjXwFfugiaRVJ34pPnOUZ3te/pub?output=csv"
moos.stream.two.2022.url <- "https://docs.google.com/spreadsheets/d/e/2PACX-1vQRXmAtoP_7I2RYEDZrdCT1LDyD8W3Thjst549srxdlWDMUYUyBjiGABd8pgtZE9Efa8b4Vgb3qtyoc/pub?output=csv"

# load in data
moos.atmo.2022 <- read.csv(url(moos.atmo.2022.url), skip = 1) 
moos.stream.one.2022 <- read.csv(url(moos.stream.one.2022.url), skip = 1) 
moos.stream.two.2022 <- read.csv(url(moos.stream.two.2022.url), skip = 1)

# cleaning df to be able to interpret and merge
moos.atmo.2022 <- moos.atmo.2022[, -c(5:11)] # removing columns that aren't date/abs pressure and temp
moos.stream.one.2022 <- moos.stream.one.2022[, -c(5:13)] # removing columns that aren't date/abs pressure and temp
moos.stream.two.2022 <- moos.stream.two.2022[, -c(5:13)] # removing columns that arent date/abs pressure and temp

# changing datetime to AK time 
moos.atmo.2022$DateTimeAK <- mdy_hms(moos.atmo.2022$Date.Time..GMT.08.00)

moos.stream.one.2022$DateTimeAK <- mdy_hms(moos.stream.one.2022$Date.Time..GMT.08.00)

moos.stream.two.2022$DateTimeAK <- mdy_hms(moos.stream.two.2022$Date.Time..GMT.08.00)

moos.stream.two.2022$DateTimeAK <- force_tz(moos.stream.two.2022$DateTimeAK, tzone = "America/Anchorage")

moos.stream.one.2022$DateTimeAK <- force_tz(moos.stream.one.2022$DateTimeAK, tzone = "America/Anchorage")

moos.atmo.2022$DateTimeAK <- force_tz(moos.atmo.2022$DateTimeAK, tzone = "America/Anchorage")

# round date to 5 minute intervals
moos.atmo.2022$DateTimeAK <- lubridate::round_date(moos.atmo.2022$DateTimeAK, "5 minutes")
moos.stream.one.2022$DateTimeAK <- lubridate::round_date(moos.stream.one.2022$DateTimeAK, "5 minutes")
moos.stream.two.2022$DateTimeAK <- lubridate::round_date(moos.stream.two.2022$DateTimeAK, "5 minutes")

# changing the names

# cleaning off original datetime 
moos.atmo.2022 <- moos.atmo.2022[, -c(2)] # removing columns that aren't date/abs pressure and temp
moos.stream.one.2022 <- moos.stream.one.2022[, -c(2)] # removing columns that aren't date/abs pressure and temp
moos.stream.two.2022 <- moos.stream.two.2022[, -c(2)] # removing columns that arent 

names(moos.atmo.2022) <- c("Site", "AirPressure", "TempC", "DateTimeAK")

names(moos.stream.one.2022) <- c("Site", "WaterPressure", "TempC", "DateTimeAK")

names(moos.stream.two.2022) <- c("Site", "WaterPressure", "TempC",  "DateTimeAK")

moos.atmo.2022 %>% filter(AirPressure > 96.8) %>% ggplot(aes(x = DateTimeAK, y = AirPressure)) +
  geom_point()

```

This is the raw atmospheric pressure that is located at MOOS. I am going to clean this up a little bit:

```{r, warning = FALSE, message = FALSE}
# cleaning erroneous points 
moos.atmo.2022 <- moos.atmo.2022 %>%
  mutate(across(c(AirPressure), 
                ~ifelse(DateTimeAK <= "2022-06-01" & AirPressure < 97.5, NA, .))) %>% filter(AirPressure > 96.5)

moos.atmo.2022 <- moos.atmo.2022 %>%
  mutate(across(c(AirPressure), 
                ~ifelse(DateTimeAK >= "2022-05-15" & DateTimeAK <= "2022-05-20" & AirPressure < 98.2, NA, .)))

moos.atmo.2022 <- moos.atmo.2022 %>%
  mutate(across(c(AirPressure), 
                ~ifelse(DateTimeAK >= "2022-05-18" & DateTimeAK <= "2022-05-20" & AirPressure < 99.1, NA, .)))

moos.atmo.2022 <- moos.atmo.2022 %>%
  mutate(across(c(AirPressure), 
                ~ifelse(DateTimeAK >= "2022-08-10" & DateTimeAK <= "2022-08-12" & AirPressure > 99.5, NA, .)))

moos.atmo.2022 <- moos.atmo.2022 %>%
  mutate(across(c(AirPressure), 
                ~ifelse(DateTimeAK >= "2022-08-10" & DateTimeAK <= "2022-08-12" & AirPressure < 99, NA, .)))

moos.atmo.2022 <- moos.atmo.2022 %>%
  mutate(across(c(AirPressure), 
                ~ifelse(DateTimeAK >= "2022-08-10" & AirPressure < 96.8, NA, .)))

moos.atmo.2022 <- moos.atmo.2022 %>% filter(DateTimeAK <= "2022-10-10 12:30:00") %>% mutate(across(c(AirPressure), 
                ~ifelse(DateTimeAK >= "2022-10-3"& DateTimeAK <= "2022-10-8" & AirPressure < 98.5, NA, .))) 

moos.atmo.2022 <- moos.atmo.2022 %>% mutate(across(c(AirPressure), 
                ~ifelse(DateTimeAK >= "2022-10-2"& DateTimeAK <= "2022-10-3" & AirPressure < 98, NA, .))) 


moos.atmo.2022 %>% filter(DateTimeAK <= "2022-10-15" & DateTimeAK >= "2022-10-01") %>% ggplot(aes(x = DateTimeAK, y = AirPressure)) +
  geom_point()

moos.atmo.2022 %>% ggplot(aes(x = DateTimeAK, y = AirPressure)) +
  geom_point()


```
This is a little better. 


Here is the uncorrected air pressure comparison between Eielson and MOOS: 

```{r, warning = FALSE, message = FALSE}
moos.atmo.2022.compare <- moos.atmo.2022

atmo.pt.2022.1 <- left_join(eielson.atmo.2022.compare, moos.atmo.2022.compare, by = "DateTimeAK")

atmo.pt.2022.1 %>% #filter(DateTimeAK >= "2022-05-01" & DateTimeAK <= "2022-05-15") %>% 
  ggplot(aes(x = DateTimeAK, y = AirPressureCorrectedMOOS)) +
  geom_line(aes(x=DateTimeAK, y=AirPressureCorrectedMOOS), color="#A6CEE3") +
  geom_line(aes(x=DateTimeAK, y=AirPressure.x), color="#FF7F00") +
  geom_line(aes(x=DateTimeAK, y=AirPressure.y), color = "red") +
  theme_classic() +
  ggtitle("Eielson Corrected(blue) & Eielson uncorrected(orange) & MOOS(red) Atmo P") 

```

Looks like we have to use the corrected pressure to get what we want for our rating curves.

We will only use pressure transducer 2 at Moose because it is more complete.

```{r, warning = FALSE, message = FALSE}
ggplot(moos.stream.two.2022, aes(x = DateTimeAK, y = WaterPressure)) +
  geom_point() +
  theme_classic()


```

This is PT2 that has the step changes due to the cleaning and then it has a gap at the end of July to beginning of August was because the memory filled up. 


```{r, warning = FALSE, message = FALSE}
# adjusting/cleaning moos.stream.two
#moos.stream.two.2022.b <- moos.stream.two.2022
#moos.stream.two.2022 <- moos.stream.two.2022.b

moos.stream.two.2022 <- moos.stream.two.2022 %>%
  mutate(across(c(WaterPressure), 
                ~ifelse(DateTimeAK <= "2022-05-25", NA, .))) # PT wasnt placed into the stream until 5/25

moos.stream.two.2022 <- moos.stream.two.2022 %>%
  mutate(across(c(WaterPressure), 
                ~ifelse(DateTimeAK >= "2022-06-01" & DateTimeAK <= "2022-07-01" & WaterPressure < 101, NA, .))) %>% filter(WaterPressure > 90)

# shifting the step change 
moos.2.before <- moos.stream.two.2022[c(1:3913), ] # 6/7 @ 14:05 we cleaned the PVC housing so we are shifting the previous data up to match after the cleaning 
moos.2.after <- moos.stream.two.2022[c(3914:40000), ]
moos.stream.two.2022[3914, 2] - moos.stream.two.2022[3913, 2] # 3.573
moos.2.before$WaterPressure <- moos.2.before[, 2] + 3.573
moos.stream.two.2022 <- full_join(moos.2.before, moos.2.after)

moos.2.before2 <- moos.stream.two.2022[c(1:25525), ] 
moos.2.mid2 <- moos.stream.two.2022[c(25531:33593), ]
moos.2.after2 <- moos.stream.two.2022[c(33593:40000), ]
moos.stream.two.2022[25525, 2] - moos.stream.two.2022[25531, 2]  # 10.918
moos.2.mid2$WaterPressure <- moos.2.mid2[, 2] - 10.918
moos.stream.two.2022.2 <- full_join(moos.2.before2, moos.2.mid2)
moos.stream.two.2022 <- full_join(moos.stream.two.2022.2, moos.2.after2)

## Bring the last chunk up half way?
moos.stream.two.2022 <- moos.stream.two.2022 %>%
  mutate(across(c(WaterPressure), 
                ~ifelse(DateTimeAK > "2022-08-01", WaterPressure + 3.897/2, .)))
#moos.2.before3 <- moos.stream.two.2022[c(1:17192), ] 
#moos.2.after3 <- moos.stream.two.2022[c(17193:40000), ]
moos.stream.two.2022[17192, 2] - moos.stream.two.2022[17211, 2] # 3.897
#moos.2.after3$WaterPressure <- moos.2.after3[, 2] + 5.389/2
#moos.stream.two.2022 <- full_join(moos.2.before3, moos.2.after3)

moos.stream.two.2022 <- moos.stream.two.2022 %>% filter(DateTimeAK < "2022-07-31" | DateTimeAK > "2022-08-02 16:45:00") %>% filter(DateTimeAK <= "2022-10-08 08:15:00")

# shifting small step change 
moos.2.before4 <- moos.stream.two.2022[c(1:5240), ]
moos.2.after4 <- moos.stream.two.2022[c(5241:40000), ]
moos.stream.two.2022[5240, 2] - moos.stream.two.2022[5241, 2] # 0.365
moos.2.after4$WaterPressure <- moos.2.after4[, 2] - 0.365
moos.stream.two.2022 <- full_join(moos.2.before4, moos.2.after4)

# shifting small step change 
moos.2.before5 <- moos.stream.two.2022[c(1:33588), ]
moos.2.after5 <- moos.stream.two.2022[c(33591:40000), ]
moos.stream.two.2022[33588, 2] - moos.stream.two.2022[33591, 2] # 0.41
moos.2.after5$WaterPressure <- moos.2.after5[, 2] - 0.41
moos.stream.two.2022 <- full_join(moos.2.before5, moos.2.after5)

moos.stream.two.2022 <- moos.stream.two.2022 %>% filter(WaterPressure < 110)

moos.stream.two.2022 %>%
  #filter(DateTimeAK > "2022-09-28 12:00:00" & DateTimeAK < "2022-09-29") %>% 
  ggplot(aes(x = DateTimeAK, y = WaterPressure)) +
  geom_point() +
  theme_classic()

```

This looks much better 

```{r, warning = FALSE, message = FALSE}
## Combine water and air pressure
# Final water pressure
moos.final.pressure.2022 <- moos.stream.two.2022


moos.final.pressure.2022 <- moos.final.pressure.2022[,-c(3,5,7)] # removing columns that are unnecessary. I only need both water pressures and mean pressure with a DateTime column 


eielson.atmo.2022 <- eielson.atmo.2022[,-c(1,3)] # i dont need site, Temp and sea_level_pressure column

eielson.atmo.2022.compare <-  eielson.atmo.2022.compare[ , -which(names(eielson.atmo.2022.compare) %in% c("Site","TempC", "sea_level_pressure", "AirPressure", "mmHG", "mmHGcorrectedMOOS","mmHGcorrectedPOKE","mmHGcorrectedSTRT","mmHGcorrectedFRCH","mmHGcorrectedVAUL"))] # removing columns I do not need

# Fill gap during end of July for our pressure data with Eielson data
atmo.pt.2022.1$moos.combo <- ifelse(atmo.pt.2022.1$DateTimeAK > "2022-07-23 17:15:00" & atmo.pt.2022.1$DateTimeAK < "2022-08-02 17:00:00", atmo.pt.2022.1$AirPressureCorrectedMOOS, atmo.pt.2022.1$AirPressure.y)

# Remove outliers
atmo.pt.2022.1 <- atmo.pt.2022.1 %>%
  mutate(across(c(moos.combo), 
                ~ifelse(DateTimeAK >= "2022-09-10" & DateTimeAK <= "2022-09-11" & moos.combo < 98.5, NA, .)))

#atmo.pt.2022.1 %>% filter(DateTimeAK > "2022-05-15") %>% 
  #filter(DateTimeAK > "2022-06-01" & DateTimeAK < "2022-09-01") %>%
 # ggplot(aes(DateTimeAK, AirPressureCorrectedMOOS)) + geom_point() #+ geom_vline(xintercept = as.POSIXct("2022-09-10")) + geom_vline(xintercept = as.POSIXct("2022-09-12"))
```

Our Moose air pressure data is so messy - it is probably more accurate to use Eielson's data.

```{r, warning = FALSE, message = FALSE}
#join the atmospheric and water pressure together

MOOS.2022 <- left_join(atmo.pt.2022.1, moos.final.pressure.2022, by = "DateTimeAK")


# Water pressure - atmospheric pressure
 MOOS.2022$difference <- MOOS.2022$WaterPressure - MOOS.2022$AirPressureCorrectedMOOS

 
 
 MOOS.2022 %>% filter(DateTimeAK > "2022-05-15") %>% 
  #filter(DateTimeAK > "2022-09-18" & DateTimeAK < "2022-09-22") %>%
  ggplot(aes(DateTimeAK, WaterPressure)) + geom_point() + geom_point(aes(DateTimeAK, AirPressureCorrectedMOOS)) + #geom_vline (xintercept = as.POSIXct("2022-09-20 20:00:00")) 
ggtitle("MOOS air and water pressure")
```
 
```{r, warning = FALSE, message = FALSE} 
# Plot difference
MOOS.2022 %>% filter(DateTimeAK > "2022-05-20") %>% 
  ggplot(aes(DateTimeAK, difference)) + geom_point() +
  ggtitle("MOOS difference")

#MOOS.2022 %>% filter(DateTimeAK > "2022-09-01" & DateTimeAK < "2022-10-15") %>% filter(difference > 5) %>% View()
```


```{r, warning = FALSE, message = FALSE}
### Plot MOOS measured Q
QSummary.MO.2022 <- QSummary.2022 %>% filter(Site =="MOOS")

ggplot(QSummary.MO.2022) +
  geom_point(aes(x = DateTimeAK, y = MeasuredQ_Ls, shape = Method, color = Site), size=3) +
  theme_classic() +
  scale_color_manual(values=c("#A6761D")) + 
  ggtitle("MOOS") 

```

```{r, warning = FALSE, message = FALSE}
# trying to merge by nearest date if we have an offset point 
MOOS.2022.dt <- setDT(MOOS.2022)
MOOS.2022.dt <- subset(MOOS.2022.dt, DateTimeAK < "2022-10-19 14:00:00") %>% na.omit()# removing rows that had dates corresponding to end of record that messed up the rolling nearest function 
QSummary.MO.2022.dt <- QSummary.MO.2022

Moose1comb.2022 <- MOOS.2022.dt[QSummary.MO.2022.dt, on = "DateTimeAK", roll = 'nearest']

## ONLY using PT 2
MOOS1.lm.2022 <- lm(Moose1comb.2022$MeasuredQ_Ls ~ Moose1comb.2022$difference)
#summary(MOOS1.lm.2022)
```

```{r, warning = FALSE, message = FALSE}

# plot rating curve 
moos.formula = y~x

ggplot(aes(x = difference, y = MeasuredQ_Ls), data = Moose1comb.2022) +
  geom_point(aes(color = Method), size = 3) +
  geom_smooth(method = "lm", se=FALSE, formula = moos.formula) +
  stat_poly_eq(formula = moos.formula,
               aes(label = paste(..eq.label.., ..rr.label.., sep = "~~~")),
               parse = TRUE) +
  theme_light() +
  ggtitle("Moose all measured Q")

```

```{r, warning = FALSE, message = FALSE}
# Remove outlier Q points
Moose1comb.2022.2 <- Moose1comb.2022 %>% filter(difference < 4 | MeasuredQ_Ls > 1000)

# plot rating curve 
moos.formula = y~x

ggplot(aes(x = difference, y = MeasuredQ_Ls), data = Moose1comb.2022.2) +
  geom_point(aes(color = Method), size = 3) +
  geom_smooth(method = "lm", se=FALSE, formula = moos.formula) +
  stat_poly_eq(formula = moos.formula,
               aes(label = paste(..eq.label.., ..rr.label.., sep = "~~~")),
               parse = TRUE) +
  theme_light() +
  ggtitle("Moose measured Q")

```
I will try removing the two low difference, high measured Q points
```{r, warning = FALSE, message = FALSE}
# Remove two low difference, high measured Q points
Moose1comb.2022.3 <- Moose1comb.2022.2 %>% filter(MeasuredQ_Ls < 1000 | MeasuredQ_Ls > 2000)

# plot rating curve 
moos.formula = y~x

ggplot(aes(x = difference, y = MeasuredQ_Ls), data = Moose1comb.2022.3) +
  geom_point(aes(color = Method), size = 3) +
  geom_smooth(method = "lm", se=FALSE, formula = moos.formula) +
  stat_poly_eq(formula = moos.formula,
               aes(label = paste(..eq.label.., ..rr.label.., sep = "~~~")),
               parse = TRUE) +
  theme_light() +
  ggtitle("Moose measured Q")

```
```{r, warning = FALSE, message = FALSE}
## Predict MOOS Q

MOOS1.lm.2022 <- lm(Moose1comb.2022.3$MeasuredQ_Ls ~ Moose1comb.2022.3$difference)

MOOS.2022.dt$pred.moos1.Q <- coef(MOOS1.lm.2022)[2] * MOOS.2022.dt$difference+ coef(MOOS1.lm.2022)[1]

MOOS.2022.dt <- MOOS.2022.dt %>% select(DateTimeAK, pred.moos1.Q) %>% filter(DateTimeAK >= "2022-05-25 08:05:00" & DateTimeAK <= "2022-10-08 16:15:00")
MOOS.2022.dt <- na_kalman(MOOS.2022.dt)

MOOS.2022.dt %>% na.omit() %>% ggplot(aes(x = DateTimeAK, y = pred.moos1.Q)) +
  geom_line(color="#A6CEE3", size=1.25) +
  geom_point(data = Moose1comb.2022, aes(x = DateTimeAK, y = MeasuredQ_Ls, shape = Method), size=3) +
  theme_classic() +
  ggtitle("Moose predicted and measured Q") +
  xlab("Date") +
  ylab("Discharge (L/s)")

```

### POKE ####

```{r, warning = FALSE, message = FALSE}

poke.stream.one.2022.url <- "https://docs.google.com/spreadsheets/d/e/2PACX-1vR8p1pdbkQBMo54XaZinGwxyzojCnlkXeZid3EFvmt9v31PFvpsa1DlWClj8aG0kkJIuU57WXl-cq7Q/pub?output=csv"
poke.stream.two.2022.url <- "https://docs.google.com/spreadsheets/d/e/2PACX-1vR-wJjf3rO8eC7bMpQZgwqFLHFQpf5qCInyWtUF1PqaCB8Z_EoM1cTHRUmWypjftREIx1rP0V6zYJxL/pub?output=csv"

# load in url
poke.stream.one.2022 <- read.csv(url(poke.stream.one.2022.url), skip = 1) 
poke.stream.two.2022 <- read.csv(url(poke.stream.two.2022.url), skip = 1) 

# cleaning df to be able to interpret and merge
poke.stream.one.2022 <- poke.stream.one.2022[, -c(5:18)] # removing columns that arent date/abs pressure and temp

poke.stream.two.2022 <- poke.stream.two.2022[, -c(5:9)] # removing columns that arent date/abs pressure and temp

# changing to AK time (It reads in as GMT but it is actually AKST )
poke.stream.one.2022$DateTimeAK <- mdy_hms(poke.stream.one.2022$Date.Time..GMT.08.00)

poke.stream.two.2022$DateTimeAK <- mdy_hms(poke.stream.two.2022$Date.Time..GMT.08.00)

poke.stream.two.2022$DateTimeAK <- force_tz(poke.stream.two.2022$DateTimeAK, tzone = "America/Anchorage")

poke.stream.one.2022$DateTimeAK <- force_tz(poke.stream.one.2022$DateTimeAK, tzone = "America/Anchorage")

# round date to 5 minute intervals
poke.stream.one.2022$DateTimeAK <- lubridate::round_date(poke.stream.one.2022$DateTimeAK, "5 minutes")
poke.stream.two.2022$DateTimeAK <- lubridate::round_date(poke.stream.two.2022$DateTimeAK, "5 minutes")

# cleaning off original datetime 
poke.stream.one.2022 <- poke.stream.one.2022[, -c(2)] # removing columns that aren't date/abs pressure and temp
poke.stream.two.2022 <- poke.stream.two.2022[, -c(2)] # removing columns that arent 


names(poke.stream.one.2022) <- c("Site", "WaterPressure", "TempC", "DateTimeAK")
names(poke.stream.two.2022) <- c("Site", "WaterPressure", "TempC", "DateTimeAK")


```


```{r, warning = FALSE, message = FALSE}
ggplot(poke.stream.one.2022, aes(x = DateTimeAK, y = WaterPressure))+
  geom_point() +
  theme_classic()

```

This is PT1....step change is air pressure and then placed in the stream. Let me clip that out 

```{r, warning = FALSE, message = FALSE}
#poke.stream.one.2022.b <- poke.stream.one.2022
#poke.stream.one.2022 <- poke.stream.one.2022.b

#adjusting/cleaning poke.stream.one
poke.stream.one.2022 <- poke.stream.one.2022 %>%
  mutate(across(c(WaterPressure), 
                ~ifelse(DateTimeAK >= "2022-05-09" & DateTimeAK <= "2022-05-18", NA, .))) # PT wasnt placed into the stream until 5/17

poke.stream.one.2022 <- poke.stream.one.2022 %>%
  mutate(across(c(WaterPressure), 
                ~ifelse(DateTimeAK >= "2022-08-27" & DateTimeAK <= "2022-08-31" & WaterPressure < 98.3, NA, .))) %>% filter( DateTimeAK <= "2022-10-07 15:30:00")

poke.stream.one.2022 <- poke.stream.one.2022 %>%
  mutate(across(c(WaterPressure), 
                ~ifelse(DateTimeAK >= "2022-10-05" & DateTimeAK <= "2022-10-07" & WaterPressure < 98, NA, .)))

poke.stream.one.2022 <- poke.stream.one.2022 %>%
  mutate(across(c(WaterPressure), 
                ~ifelse(DateTimeAK >= "2022-10-05" & DateTimeAK <= "2022-10-07" & WaterPressure < 98, NA, .))) %>% 
  filter(DateTimeAK > "2022-08-01 16:15:00" | DateTimeAK < "2022-08-01 00:00:00") %>%
  filter(DateTimeAK != "2022-08-07 19:00:00") 

# shifting small step change 
poke.2.before <- poke.stream.one.2022[c(1:16756), ]
poke.2.after <- poke.stream.one.2022[c(16758:40000), ]
poke.stream.one.2022[16756, 2] - poke.stream.one.2022[16758, 2] # 0.39
poke.2.after$WaterPressure <- poke.2.after[, 2] + 0.39
poke.stream.one.2022 <- full_join(poke.2.before, poke.2.after)

# shifting larger step change 
poke.1.before2 <- poke.stream.one.2022[c(1:8125), ]
poke.1.after2 <- poke.stream.one.2022[c(8150:40000), ]
poke.stream.one.2022[8150, 2] - poke.stream.one.2022[8125, 2] # 1.55
poke.1.after2$WaterPressure <- poke.1.after2[, 2] + 1.55
poke.stream.one.2022 <- full_join(poke.1.before2, poke.1.after2)


poke.stream.one.2022 %>% #filter(DateTimeAK > "2022-08-07" & DateTimeAK < "2022-08-15") %>%
  ggplot(aes(x = DateTimeAK, y = WaterPressure))+
  geom_point() +
  theme_classic()

```

Clean PT2
```{r, warning = FALSE, message = FALSE}
poke.stream.two.2022 <- poke.stream.two.2022 %>%
  mutate(across(c(WaterPressure), 
                ~ifelse(DateTimeAK >= "2022-09-17" & WaterPressure < 98, NA, .))) %>%
  filter(DateTimeAK <= "2022-10-07 15:35:00")

poke.stream.two.2022 %>% ggplot(aes(x = DateTimeAK, y = WaterPressure))+
  geom_point() +
  theme_classic()

```

This is PT2...we only have data from 8/1 because of our musical chairs situation. We got two PTs back from onset so we deployed a second PT at POKE.

```{r, warning = FALSE, message = FALSE}

# merge to one 
poke.final.pressure.2022 <- left_join(poke.stream.one.2022, poke.stream.two.2022, by = c("DateTimeAK"))
poke.final.pressure.2022$MeanPressure <- rowMeans(poke.final.pressure.2022[,c(2,6)], na.rm = TRUE)

poke.final.pressure.2022 %>% ggplot() + geom_point(aes(DateTimeAK, WaterPressure.x)) + geom_point(aes(DateTimeAK, WaterPressure.y), color = "red", cex = 0.5)
```
It looks like we should use PT1 before August 1st (black) and PT2 after August 1st (red).
```{r, warning = FALSE, message = FALSE}
## Use PT1 before August 1st and PT2 after August 1st
# Shift PT2 up to match August PT1
poke.final.pressure.2022 %>% filter(DateTimeAK > "2022-08-01" & DateTimeAK < "2022-08-15") %>% summarise(mean(WaterPressure.x - WaterPressure.y)) #2.62398	

poke.final.pressure.2022 <- poke.final.pressure.2022 %>%
  mutate(WaterPressure.merged = ifelse(DateTimeAK <= "2022-08-01", WaterPressure.x, WaterPressure.y))

# September step change
poke.before <- poke.final.pressure.2022[c(1:37665), ]
poke.after <- poke.final.pressure.2022[c(37705:40000), ]
poke.final.pressure.2022[37705, 9] - poke.final.pressure.2022[37665, 9] # 0.374
poke.after$WaterPressure.merged <- poke.after[, 9] + 0.374
poke.final.pressure.2022 <- rbind(poke.before, poke.after)

# End of August step change... move after data down all the way?
poke.before <- poke.final.pressure.2022[c(1:29719), ]
poke.after <- poke.final.pressure.2022[c(29720:40000), ]
poke.final.pressure.2022[29720, 9] - poke.final.pressure.2022[29719, 9] # 0.858
poke.after$WaterPressure.merged <- poke.after[, 9] - 0.858
poke.final.pressure.2022 <- rbind(poke.before, poke.after)


poke.final.pressure.2022 %>% #filter(DateTimeAK > "2022-08-29" & DateTimeAK < "2022-08-29 17:00:00") %>% 
  ggplot() + geom_point(aes(DateTimeAK, WaterPressure.merged))

#poke.final.pressure.2022 %>% filter(DateTimeAK > "2022-06-05" & DateTimeAK < "2022-06-06 17:00:00") %>% View()
```

Shift after gap up halfway like I did with Moose?

```{r, warning = FALSE, message = FALSE}
# Join the two atmospheric and water pressure together
poke.final.pressure.2022.2 <- poke.final.pressure.2022 %>% filter(!WaterPressure.merged %in% NA)
POKE.2022 <- left_join(eielson.atmo.2022.compare, poke.final.pressure.2022.2, by = "DateTimeAK") 

## Bring the last chunk up half way?
101.250-98.134
POKE.2022 <- POKE.2022 %>%
 mutate(across(c(WaterPressure.merged), 
                ~ifelse(DateTimeAK > "2022-07-30", WaterPressure.merged + 3.116*.5, .)))

# Water pressure - atmospheric pressure 
POKE.2022$difference <- POKE.2022$WaterPressure.merged - POKE.2022$AirPressureCorrectedPOKE

# Plot air and water pressure
  
POKE.2022 %>% #filter(DateTimeAK >"2022-09-26 10:00:00" & DateTimeAK < "2022-09-26 20:00:00") %>%
  filter(DateTimeAK > "2022-05-25") %>%
  ggplot(aes(DateTimeAK, WaterPressure.merged)) + geom_point() + geom_point(aes(DateTimeAK, AirPressureCorrectedPOKE), color = "red") + #geom_point(aes(color = Method, x = DateTimeAK, y = WaterPressure.merged), data = Poker1comb.2022[c(19,20),])
  ggtitle("POKE air and water pressure")
```

```{r, warning = FALSE, message = FALSE} 
# Plot difference
POKE.2022 %>% filter(DateTimeAK > "2022-05-15") %>% 
  ggplot(aes(DateTimeAK, difference)) + geom_point() +
  ggtitle("POKE difference")
```

```{r, warning = FALSE, message = FALSE}
### Filter POKE ###
QSummary.PO.2022 <- QSummary.2022 %>% filter(Site =="POKE")

ggplot(QSummary.PO.2022) +
  geom_point(aes(x = DateTimeAK, y = MeasuredQ_Ls, shape = Method, color = Site), size=3) +
  theme_classic() +
  scale_color_manual(values=c("#6A3D9A")) + 
  ggtitle("POKE") 

```

```{r, warning = FALSE, message = FALSE}
# Merge by nearest date if we have an offset point 
POKE.2022.dt <- setDT(POKE.2022) %>% filter(!difference %in% NA)
QSummary.PO.2022.dt <- QSummary.PO.2022 %>% filter(DateTimeAK > "2022-05-17")

Poker1comb.2022 <- POKE.2022.dt[QSummary.PO.2022.dt, on = "DateTimeAK", roll = 'nearest']


```

```{r, warning = FALSE, message = FALSE}
### Rating Curve ###
poke.formula <- y ~ x
ggplot(aes(x = difference, y = MeasuredQ_Ls), data = Poker1comb.2022) +
  geom_point(aes(color = Method), size = 3) +
  geom_smooth(method = "lm", se=FALSE, formula = poke.formula) +
  stat_poly_eq(formula = poke.formula,
               aes(label = paste(..eq.label.., ..rr.label.., sep = "~~~")),
               parse = TRUE) +
  theme_light() +
  ggtitle("Poker all measured Q")

```

This is the rating curve. We are missing 5/9 and 5/17 YSI because we didn't have our Pressure Transducers in yet.

I am not sure what is going on here. I plotted every single pressure point that is matched with a Q measurement and they all look reasonable/are not outliers.

I will remove two points.

```{r, warning = FALSE, message = FALSE}
# Remove two high Q points points
Poker1comb.2022.2 <- Poker1comb.2022 %>% filter(MeasuredQ_Ls < 700 | difference > 4)
### Rating Curve ###
poke.formula <- y ~ x
ggplot(aes(x = difference, y = MeasuredQ_Ls), data = Poker1comb.2022.2) +
  geom_point(aes(color = Method), size = 3) +
  geom_smooth(method = "lm", se=FALSE, formula = poke.formula) +
  stat_poly_eq(formula = poke.formula,
               aes(label = paste(..eq.label.., ..rr.label.., sep = "~~~")),
               parse = TRUE) +
  theme_light() +
  ggtitle("Poker measured Q")

```

I will try curves for just wading rod with quadratic relationship.

```{r, warning = FALSE, message = FALSE}
### Rating Curve ###
poke.formula <- y ~ poly(x, 2, raw = TRUE)
Poker1comb.2022.2 %>% filter(Method == "Wading Rod") %>% ggplot(aes(x = difference, y = MeasuredQ_Ls)) +
  geom_point(aes(color = Method), size = 3) +
  geom_smooth(method = "lm", se=FALSE, formula = poke.formula) +
  stat_poly_eq(formula = poke.formula,
               aes(label = paste(..eq.label.., ..rr.label.., sep = "~~~")),
               parse = TRUE) +
  theme_light() +
  ggtitle("Poker measured Q")

```
Should we add a few YSI points back in?
```{r, warning = FALSE, message = FALSE}
### Rating Curve ###

poke.formula <- y ~ poly(x, 2, raw = TRUE)
Poker1comb.2022.3 <- Poker1comb.2022.2 %>% filter(difference > 2.5 | MeasuredQ_Ls < 450) 
Poker1comb.2022.3 %>% ggplot(aes(x = difference, y = MeasuredQ_Ls)) +
  geom_point(aes(color = Method), size = 3) +
  geom_smooth(method = "lm", se=FALSE, formula = poke.formula) +
  stat_poly_eq(formula = poke.formula,
               aes(label = paste(..eq.label.., ..rr.label.., sep = "~~~")),
               parse = TRUE) +
  theme_light() +
  ggtitle("Poker measured Q")

```


```{r, warning = FALSE, message = FALSE}
## Predict POKE Q
POKE1.lm.2022 <- lm(Poker1comb.2022.3$MeasuredQ_Ls ~ Poker1comb.2022.3$difference + I(Poker1comb.2022.3$difference^2))


POKE.2022.dt$pred.poke.Q <- coef(POKE1.lm.2022)[2] * POKE.2022.dt$difference + I(coef(POKE1.lm.2022)[3] * POKE.2022.dt$difference^2)+coef(POKE1.lm.2022)[1]

POKE.2022.dt <- POKE.2022.dt %>% select(DateTimeAK, pred.poke.Q)
POKE.2022.dt <- na_kalman(POKE.2022.dt)

POKE.2022.dt %>% na.omit() %>% ggplot(aes(x = DateTimeAK, y = pred.poke.Q)) +
  geom_line(color="#A6CEE3", size=1.25) +
  geom_point(data = Poker1comb.2022, aes(x = DateTimeAK, y = MeasuredQ_Ls, color = Method), size=3) +
  theme_classic() +
  ggtitle("Poker predicted and measured Q") +
  xlab("Date") +
  ylab("Discharge (L/s)")

```

### STRT ###
```{r, warning = FALSE, message = FALSE}
strt.stream.one.2022.url <- "https://docs.google.com/spreadsheets/d/e/2PACX-1vS4XSmuumKD-j1aDhpA1gfyfrpqUiJUTuvcP9UGrgagvIrzlGYWk71hl0zAC8g8GHqOm1ONjWOpO_So/pub?output=csv" # WL
strt.stream.two.2022.url <- "https://docs.google.com/spreadsheets/d/e/2PACX-1vRhNn42-Jr1Y3aTFfMPiRxKrNZZjHeBBxkCmVcLVPQEKBf4qg_1Pw4nyUBr3mDwtEE8NKGIbS7kNSrS/pub?output=csv" #WR
strt.atmo.2022.url <- "https://docs.google.com/spreadsheets/d/e/2PACX-1vQxotkNZ6zyvUi51XOjNPumqSvwGfsZMJc7I6-QXBELHY7msBzAaqvEHV41A88Lt0I1Ga-l1343Q1cr/pub?output=csv"
# load in data 
strt.stream.one.2022 <- read.csv(url(strt.stream.one.2022.url), skip = 1) 
strt.stream.two.2022 <- read.csv(url(strt.stream.two.2022.url), skip = 1) 
strt.atmo.2022 <- read.csv(url(strt.atmo.2022.url), skip = 1) 

# clean for merging purposes
strt.stream.one.2022 <- strt.stream.one.2022[, -c(4,6:19)] # removing columns that arent date/abs pressure and temp

strt.stream.two.2022 <- strt.stream.two.2022[, -c(5:12)] # removing columns that arent date/abs pressure and temp

strt.atmo.2022 <- strt.atmo.2022[,-c(4:9)]

# changing to AK time (It reads in as GMT but it is actually AKST )
strt.stream.one.2022$DateTimeAK <- mdy_hms(strt.stream.one.2022$Date.Time..GMT.08.00)

strt.stream.two.2022$DateTimeAK <- mdy_hms(strt.stream.two.2022$Date.Time..GMT.08.00)
strt.atmo.2022$DateTimeAK <- mdy_hms(strt.atmo.2022$Date.Time..GMT.08.00)

strt.stream.two.2022$DateTimeAK <- force_tz(strt.stream.two.2022$DateTimeAK, tzone = "America/Anchorage")

strt.stream.one.2022$DateTimeAK <- force_tz(strt.stream.one.2022$DateTimeAK, tzone = "America/Anchorage")

strt.atmo.2022$DateTimeAK <- force_tz(strt.atmo.2022$DateTimeAK, tzone = "America/Anchorage")


# round date to 5 minute intervals
#strt.stream.one.2022$DateTimeAK <- lubridate::round_date(strt.stream.one.2022$DateTimeAK, "5 minutes")
#strt.stream.two.2022$DateTimeAK <- lubridate::round_date(strt.stream.two.2022$DateTimeAK, "5 minutes")

# cleaning off original datetime 
strt.stream.one.2022 <- strt.stream.one.2022[, -c(2)] # removing columns that aren't date/abs pressure and temp
strt.stream.two.2022 <- strt.stream.two.2022[, -c(2)] # removing columns that arent 
strt.atmo.2022 <- strt.atmo.2022[,-c(2)]

names(strt.stream.one.2022) <- c("Site","WaterPressure", "TempC", "DateTimeAK")

names(strt.stream.two.2022) <- c("Site","WaterPressure", "TempC", "DateTimeAK")

names(strt.atmo.2022) <- c("Site", "AirPressureSTRT", "DateTimeAK")

ggplot(strt.stream.one.2022, aes(x = DateTimeAK, y = WaterPressure))+
  geom_point() +
  theme_classic()

```

This is PT1 for STRT raw. Looking at how low the PT data is I am NOT going to trust this one and take it out of our analysis 
 
 
```{r, warning = FALSE, message = FALSE}
strt.stream.two.2022 %>% filter(DateTimeAK > "2022-06-03" & DateTimeAK < "2022-06-04" ) %>% ggplot(aes(x = DateTimeAK, y = WaterPressure))+
  geom_point() +
  theme_classic()

```
This PT has SO much noise. I am going to round into 30 minute intervals.
```{r, warning = FALSE, message = FALSE}
# Take average at 60 min interval
strt.stream.two.2022$DateTimeAK <- lubridate::round_date(strt.stream.two.2022$DateTimeAK, "60 minutes")
# Take average pressure
strt.stream.two.2022 <- strt.stream.two.2022 %>% group_by(DateTimeAK) %>% summarise(DateTimeAK = unique(DateTimeAK), WaterPressure = mean(WaterPressure))

strt.stream.two.2022 %>% filter(DateTimeAK > "2022-06-03" & DateTimeAK < "2022-06-04" ) %>% ggplot(aes(x = DateTimeAK, y = WaterPressure))+
  geom_point() +
  theme_classic()
```
That looks more reasonable. I need to remove out of water points (anything before 6/2) and clean any erroneous points


```{r, warning = FALSE, message = FALSE}
#strt.stream.two.2022.b <- strt.stream.two.2022
#strt.stream.two.2022 <- strt.stream.two.2022.b

#adjusting/cleaning STRT 2
strt.stream.two.2022 <- strt.stream.two.2022 %>%
  mutate(across(c(WaterPressure), 
                ~ifelse(DateTimeAK >= "2022-05-09" & DateTimeAK <= "2022-06-03", NA, .))) # PT wasnt placed into the stream until 6/3

strt.stream.two.2022 <- strt.stream.two.2022 %>%
  mutate(across(c(WaterPressure), 
                ~ifelse(DateTimeAK >= "2022-05-09" & DateTimeAK <= "2022-10-03" &
      WaterPressure < 100, NA, .))) %>%
      filter(WaterPressure > 100)

strt.stream.two.2022 <- strt.stream.two.2022 %>% filter(DateTimeAK < "2022-08-01 00:00:00" | DateTimeAK > "2022-08-10 22:30:00")

strt.stream.two.2022 <- strt.stream.two.2022 %>%
  mutate(across(c(WaterPressure), 
                ~ifelse(DateTimeAK >= "2022-08-15 12:00:00" & DateTimeAK <= "2022-08-17" & WaterPressure > 102.45, NA, .)))

strt.stream.two.2022 %>% #filter(DateTimeAK > "2022-10-01" & DateTimeAK < "2022-10-20" ) %>%
  ggplot(aes(x = DateTimeAK, y = WaterPressure))+
  geom_point() +
  theme_classic()

```

This looks better

``` {r, warning = FALSE, message = FALSE}
# merge to one 
strt.final.pressure.2022 <- strt.stream.two.2022 # the first PT is crap

```

Clean and plot our measured air pressure

```{r, warning = FALSE, message = FALSE, include = FALSE}
#Clean and plot our measured air pressure
strt.atmo.2022 <- strt.atmo.2022 %>% filter(AirPressureSTRT > 96)

strt.atmo.2022 <- strt.atmo.2022 %>%
  mutate(across(c(AirPressureSTRT), 
                ~ifelse(DateTimeAK <= "2022-06-01" & AirPressureSTRT < 98, NA, .))) %>% filter( DateTimeAK <= "2022-09-10")

strt.atmo.2022 %>% ggplot() +  geom_point(aes(DateTimeAK, AirPressureSTRT), color = "red")
```

```{r, warning = FALSE, message = FALSE}
# Plot STRT measured and Eilson air pressure
STRT.atmo.2022.compare <- full_join(eielson.atmo.2022.compare, strt.atmo.2022, by = "DateTimeAK")

STRT.atmo.2022.compare %>% filter(DateTimeAK > "2022-05-01") %>% ggplot() + geom_point(aes(DateTimeAK, AirPressureCorrectedSTRT)) + 
  geom_point(aes(DateTimeAK, AirPressureSTRT), color = "red") +
  ggtitle("STRT air and water pressure")
```

```{r, include = FALSE}
## Use measured air pressure when possible
#STRT.atmo.2022.compare <- STRT.atmo.2022.compare %>% select(DateTimeAK, AirPressureCorrectedSTRT, AirPressureSTRT )

  ### Using mostly our air pressure data with gap filled in by Eilson:
#STRT.atmo.2022.compare$strt.combo <- c()
#STRT.atmo.2022.compare<- STRT.atmo.2022.compare %>%
#  mutate(strt.combo = ifelse(DateTimeAK <= "2022-05-18" | DateTimeAK >= "2022-06-03", #AirPressureSTRT, AirPressureCorrectedSTRT))

#STRT.atmo.2022.compare<- STRT.atmo.2022.compare %>%
#  mutate(across(c(strt.combo), 
#                ~ifelse(DateTimeAK >= "2022-07-18" & DateTimeAK <= "2022-09-03" | DateTimeAK >= "2022-09-08", AirPressureCorrectedSTRT, .)))

#STRT.atmo.2022.compare %>% filter(DateTimeAK > "2022-05-01") %>% ggplot() + geom_point(aes(DateTimeAK, strt.combo)) #+ geom_point(aes(DateTimeAK, AirPressureCorrectedSTRT), color = "red", cex = 0.5)
```

Our air pressure is so messy: lets use Eielson air pressure
```{r, warning = FALSE, message = FALSE}
# join the two atmospheric and water pressure together
STRT.2022 <- left_join(eielson.atmo.2022.compare, strt.final.pressure.2022, by = "DateTimeAK")

# Water pressure - atmospheric pressure 
STRT.2022$difference <- STRT.2022$WaterPressure - STRT.2022$AirPressureCorrectedSTRT

STRT.2022 <-  STRT.2022 %>% filter(!difference %in% NA)

```

```{r, warning = FALSE, message = FALSE}
### Filter STRT ###
QSummary.ST.2022 <- QSummary.2022 %>% filter(Site =="STRT")

ggplot(QSummary.ST.2022) +
  geom_point(aes(x = DateTimeAK, y = MeasuredQ_Ls, color = Method), size=3) +
  theme_classic() +
  ggtitle("STRT") 

```

```{r, warning = FALSE, message = FALSE}
# trying to merge by nearest date if we have an offset point 
STRT.2022.dt <- setDT(STRT.2022)
QSummary.ST.2022.dt <- QSummary.ST.2022

Stuart1comb.2022 <- STRT.2022.dt[QSummary.ST.2022.dt, on = "DateTimeAK", roll = 'nearest']

```

```{r}
### Filter STRT ###
strt.formula <- y ~ x

ggplot(aes(x = difference, y = MeasuredQ_Ls), data = Stuart1comb.2022) +
  geom_point(aes(color = Method), size = 3) +
  geom_smooth(method = "lm", se=FALSE, formula = strt.formula) +
  stat_poly_eq(formula = strt.formula,
               aes(label = paste(..eq.label.., ..rr.label.., sep = "~~~")),
               parse = TRUE) +
  theme_light() +
  ggtitle("Stuart all measured Q")

```

Not so bad. Stuart looks like a quadratic relationship might fit better.

```{r}
strt.formula <- y ~ poly(x, 2, raw = TRUE)

ggplot(aes(x = difference, y = MeasuredQ_Ls), data = Stuart1comb.2022) +
  geom_point(aes(color = Method), size = 3) +
  geom_smooth(method = "lm", se=FALSE, formula = strt.formula) +
  stat_poly_eq(formula = strt.formula,
               aes(label = paste(..eq.label.., ..rr.label.., sep = "~~~")),
               parse = TRUE) +
  theme_light() +
  ggtitle("Stuart measured Q")
```

The relationship is not strong at low Q. Lets remove the two points with difference > 4.8 and MeasuredQ_Ls < 800.

```{r}
strt.formula <- y ~ poly(x, 2, raw = TRUE)
Stuart1comb.2022.2 <- Stuart1comb.2022 %>% filter(difference < 4.8 | MeasuredQ_Ls > 800)
ggplot(aes(x = difference, y = MeasuredQ_Ls), data = Stuart1comb.2022.2) +
  geom_point(aes(color = Method), size = 3) +
  geom_smooth(method = "lm", se=FALSE, formula = strt.formula) +
  stat_poly_eq(formula = strt.formula,
               aes(label = paste(..eq.label.., ..rr.label.., sep = "~~~")),
               parse = TRUE) +
  theme_light() +
  ggtitle("Stuart measured Q")
```

```{r, message = FALSE, warning = FALSE}
## Predict STRT Q
STRT1.lm.2022 <- lm(Stuart1comb.2022.2$MeasuredQ_Ls ~ Stuart1comb.2022.2$difference + I(Stuart1comb.2022.2$difference^2))
summary(STRT1.lm.2022)

STRT.2022.dt$pred.strt1.Q <- coef(STRT1.lm.2022)[2] * STRT.2022.dt$difference + coef(STRT1.lm.2022)[3] * I(STRT.2022.dt$difference^2) + coef(STRT1.lm.2022)[1]

STRT.2022.dt %>% na.omit() %>% ggplot(aes(x = DateTimeAK, y = pred.strt1.Q)) +
  geom_line(color="#A6CEE3", size=1.25) +
  geom_point(data = Stuart1comb.2022, aes(x = DateTimeAK, y = MeasuredQ_Ls, color = Method), size=3) +
  theme_classic() +
  ggtitle("STRT predicted and measured Q") +
  xlab("Date") +
  ylab("Discharge (L/s)") 

```




I'll try a curve with just wading rod points.

```{r}
strt.formula <- y ~ poly(x, 2, raw = TRUE)
Stuart1comb.2022.3 <- Stuart1comb.2022 %>% filter(difference < 4.8 | MeasuredQ_Ls > 800, Method == "Wading Rod")
ggplot(aes(x = difference, y = MeasuredQ_Ls), data = Stuart1comb.2022.3) +
  geom_point(aes(color = Method), size = 3) +
  geom_smooth(method = "lm", se=FALSE, formula = strt.formula) +
  stat_poly_eq(formula = strt.formula,
               aes(label = paste(..eq.label.., ..rr.label.., sep = "~~~")),
               parse = TRUE) +
  theme_light() +
  ggtitle("Stuart measured Q")
```

Have we cheated? Let me check how low the R2 is when difference < 5.

```{r}
strt.formula <- y ~ x
Stuart1comb.2022.4 <- Stuart1comb.2022 %>% filter(difference < 4.8 | MeasuredQ_Ls > 800, difference < 5, Method == "Wading Rod")
ggplot(aes(x = difference, y = MeasuredQ_Ls), data = Stuart1comb.2022.4) +
  geom_point(aes(color = Method), size = 3) +
  geom_smooth(method = "lm", se=FALSE, formula = strt.formula) +
  stat_poly_eq(formula = strt.formula,
               aes(label = paste(..eq.label.., ..rr.label.., sep = "~~~")),
               parse = TRUE) +
  theme_light() +
  ggtitle("Stuart measured Q")
```

Here is the predicted Q using the Q curve with all but one wading rod point.

```{r, message = FALSE, warning = FALSE}
## Predict STRT Q
STRT1.lm.2022.2 <- lm(Stuart1comb.2022.3$MeasuredQ_Ls ~ Stuart1comb.2022.3$difference + I(Stuart1comb.2022.3$difference^2))
summary(STRT1.lm.2022.2)

STRT.2022.dt$pred.strt1.Q.2 <- coef(STRT1.lm.2022.2)[2] * STRT.2022.dt$difference + coef(STRT1.lm.2022.2)[3] * I(STRT.2022.dt$difference^2) + coef(STRT1.lm.2022.2)[1]

STRT.2022.dt %>% na.omit() %>% ggplot(aes(x = DateTimeAK, y = pred.strt1.Q.2)) +
  geom_line(color="#A6CEE3", size=1.25) +
  geom_point(data = Stuart1comb.2022, aes(x = DateTimeAK, y = MeasuredQ_Ls, color = Method), size=3) +
  theme_classic() +
  ggtitle("STRT predicted and measured Q") +
  xlab("Date") +
  ylab("Discharge (L/s)") 

```
Is this better than the first one?


### FRCH ###

```{r, message = FALSE, warning = FALSE}
frch.stream.one.2022.url <- "https://docs.google.com/spreadsheets/d/e/2PACX-1vRkT5GIhFY4nLblzPi4Upc8y6Pk2k4vXLSGAkFyMhLowsCmct0fZ5rxm-vd85RfFr7YLrCuuSiOqQbL/pub?output=csv"
frch.stream.two.2022.url <-  "https://docs.google.com/spreadsheets/d/e/2PACX-1vRiDAbzBj_jHk1Hd3iM7fFvzMrRCSF9fbKTcmQD_dUFGOjoIQuBZBKV4KdNhfevLOq0Udch0LbWiKXw/pub?output=csv"

# load in url
frch.stream.one.2022 <- read.csv(url(frch.stream.one.2022.url), skip = 1) 
frch.stream.two.2022 <- read.csv(url(frch.stream.two.2022.url), skip = 1) 

# clean for merging purposes
frch.stream.one.2022 <- frch.stream.one.2022[, -c(5:13)] # removing columns that arent date/abs pressure and temp

frch.stream.two.2022 <- frch.stream.two.2022[, -c(5:14)] # removing columns that arent date/abs pressure and temp

# changing to AK time (It reads in as GMT but it is actually AKST )
frch.stream.one.2022$DateTimeAK <- mdy_hms(frch.stream.one.2022$Date.Time..GMT.08.00)

frch.stream.two.2022$DateTimeAK <- mdy_hms(frch.stream.two.2022$Date.Time..GMT.08.00)

frch.stream.two.2022$DateTimeAK <- force_tz(frch.stream.two.2022$DateTimeAK, tzone = "America/Anchorage")

frch.stream.one.2022$DateTimeAK <- force_tz(frch.stream.one.2022$DateTimeAK, tzone = "America/Anchorage")

# cleaning off original datetime 
frch.stream.one.2022 <- frch.stream.one.2022[, -c(2)] # removing columns that aren't date/abs pressure and temp
frch.stream.two.2022 <- frch.stream.two.2022[, -c(2)] # removing columns that arent 

names(frch.stream.one.2022) <- c("Site", "WaterPressure", "TempC", "DateTimeAK")

names(frch.stream.two.2022) <- c("Site", "WaterPressure", "TempC", "DateTimeAK")

# Take average at 30 min interval
frch.stream.two.2022$DateTimeAK <- lubridate::round_date(frch.stream.two.2022$DateTimeAK, "30 minutes")
frch.stream.one.2022$DateTimeAK <- lubridate::round_date(frch.stream.one.2022$DateTimeAK, "30 minutes")
frch.stream.two.2022 <- frch.stream.two.2022 %>% group_by(DateTimeAK) %>% summarise(DateTimeAK = unique(DateTimeAK), WaterPressure = mean(WaterPressure))
frch.stream.one.2022 <- frch.stream.one.2022 %>% group_by(DateTimeAK) %>% summarise(DateTimeAK = unique(DateTimeAK), WaterPressure = mean(WaterPressure))


# merge to one 
frch.final.pressure.2022 <- left_join(frch.stream.one.2022, frch.stream.two.2022, by = c("DateTimeAK"))


```


```{r, , message = FALSE, warning = FALSE}
ggplot(frch.stream.one.2022, aes(x = DateTimeAK, y = WaterPressure))+
  geom_point() +
  theme_classic()

```

This looks like the best one yet...we need to remove the out of water points 

```{r, message = FALSE, warning = FALSE}
frch.stream.one.2022 <- frch.stream.one.2022 %>%
  mutate(across(c(WaterPressure), 
                ~ifelse(DateTimeAK >= "2022-05-09" & DateTimeAK <= "2022-05-12", NA, .))) # PT wasnt placed into the stream until 5/12

frch.stream.one.2022 <- frch.stream.one.2022 %>%
  mutate(across(c(WaterPressure), 
                ~ifelse(DateTimeAK >= "2022-08-01" & DateTimeAK <= "2022-08-15" &
  WaterPressure < 102, NA, .))) %>% filter(WaterPressure > 98.4) # PT wasnt placed into the stream until 5/12

frch.stream.one.2022 <- frch.stream.one.2022 %>% filter(DateTimeAK < "2022-10-10 10:30:00")

ggplot(frch.stream.one.2022, aes(x = DateTimeAK, y = WaterPressure))+
  geom_point() +
  theme_classic()

```

This looks better 

```{r, message = FALSE, warning = FALSE}
ggplot(frch.stream.two.2022, aes(x = DateTimeAK, y = WaterPressure))+
  geom_point() +
  theme_classic()

```

PT2 also looks good...let me remove that one point in august that is below everything else

```{r, message = FALSE, warning = FALSE}
frch.stream.two.2022 <- frch.stream.two.2022 %>%
  mutate(across(c(WaterPressure), 
                ~ifelse(DateTimeAK >= "2022-08-01" & DateTimeAK <= "2022-08-15" &
  WaterPressure < 100, NA, .))) %>% filter(WaterPressure > 98.4)# PT wasnt placed into the stream until 5/12

# Shift step in August
frch2.before <- frch.stream.two.2022[c(1:2685), ]
frch2.after <- frch.stream.two.2022[c(2687:40000), ]
frch.stream.two.2022[2685, 2] - frch.stream.two.2022[2687, 2] # 1.5485
frch2.after$WaterPressure <- frch2.after$WaterPressure + 1.5485
frch.stream.two.2022 <- rbind(frch2.before, frch2.after)

frch.stream.two.2022 <- frch.stream.two.2022 %>% filter(DateTimeAK < "2022-10-10 10:30:00")

frch.stream.two.2022 %>% #filter(DateTimeAK > "2022-10-05") %>% 
  ggplot(aes(x = DateTimeAK, y = WaterPressure))+
  geom_point() +
  theme_classic()

```


```{r, message = FALSE, warning = FALSE}
# Checking closeness between two PTs
frch.pt.both <- full_join(frch.stream.one.2022, frch.stream.two.2022, by = "DateTimeAK")

ggplot(aes(x = DateTimeAK, y = WaterPressure.x), data = frch.pt.both) +
  geom_point(aes(x=DateTimeAK, y=WaterPressure.x), data = frch.pt.both, color="#A6CEE3") +
  geom_point(aes(x=DateTimeAK, y=WaterPressure.y), data = frch.pt.both, color="#FF7F00") +
  theme_classic() +
  ggtitle("FRCH PT1(blue) & FRCH PT2(orange) Water Pressure") 

```

They look the same. Lets use PT1 except to fill the gap in July.

```{r, message = FALSE, warning = FALSE}
frch.pt.both$WaterPressure.merged <- ifelse(frch.pt.both$DateTimeAK >= "2022-07-23 17:00:00" & frch.pt.both$DateTimeAK <= "2022-08-02 12:00:00", frch.pt.both$WaterPressure.y, frch.pt.both$WaterPressure.x)


frch.pt.both %>% filter(DateTimeAK > "2022-07-01" & DateTimeAK < "2022-08-01") %>%
  ggplot(aes(x = DateTimeAK, y = WaterPressure.merged)) +
  geom_point()
```

```{r, message = FALSE, warning = FALSE}
## Clean merged water pressure data

# Shift step in July
frch.before <- frch.pt.both[c(1:3488), ]
frch.after <- frch.pt.both[c(3489:40000), ]
frch.pt.both[3488, 4] - frch.pt.both[3489, 4] # 1.914
frch.after$WaterPressure.merged <- frch.after$WaterPressure.merged + 1.914
frch.pt.both <- rbind(frch.before, frch.after)

frch.pt.both <- frch.pt.both %>% filter(!DateTimeAK %in% NA)

frch.pt.both %>% #filter(DateTimeAK > "2022-08-01" & DateTimeAK < "2022-08-05") %>%
  ggplot(aes(x = DateTimeAK, y = WaterPressure.merged)) +
  geom_point()
```

```{r, message = FALSE, warning = FALSE}
# join the two atmospheric and water pressure together

frch.final.pressure.2022 <- frch.pt.both

FRCH.2022 <- left_join(eielson.atmo.2022.compare, frch.final.pressure.2022, by = "DateTimeAK")


# Water pressure - atmospheric pressure 
FRCH.2022$difference <- FRCH.2022$WaterPressure.merged - FRCH.2022$AirPressureCorrectedFRCH

names(FRCH.2022)[names(FRCH.2022) == 'Site.x'] <- 'Site'

FRCH.2022$Site <- "FRCH"

FRCH.2022 %>% filter(DateTimeAK > "2022-05-15") %>% 
  #filter(DateTimeAK > "2022-09-18" & DateTimeAK < "2022-09-22") %>%
  ggplot(aes(DateTimeAK, WaterPressure.merged)) + geom_point() + geom_point(aes(DateTimeAK, AirPressureCorrectedFRCH)) + #geom_vline (xintercept = as.POSIXct("2022-09-20 20:00:00")) 
ggtitle("FRCH air and water pressure")
```

```{r, message = FALSE, warning = FALSE}
### Filter FRCH ###
QSummary.FR.2022 <- QSummary.2022 %>% filter(Site =="FRCH")

ggplot(QSummary.FR.2022) +
  geom_point(aes(x = DateTimeAK, y = MeasuredQ_Ls, shape = Method, color = Site), size=3) +
  theme_classic() +
  scale_color_manual(values=c("#FF7F00")) + 
  ggtitle("FRCH") 

```


```{r, message = FALSE, warning = FALSE}
# trying to merge by nearest date if we have an offset point 
FRCH.2022.dt <- setDT(FRCH.2022)
QSummary.FR.2022.dt <- QSummary.FR.2022

French1comb.2022 <- FRCH.2022.dt[QSummary.FR.2022.dt, on = "DateTimeAK", roll = 'nearest']

FRCH1.lm.2022 <- lm(French1comb.2022$MeasuredQ_Ls ~ French1comb.2022$difference)

```

```{r, message = FALSE, warning = FALSE}
# rating curve # 
frch.formula <- y ~ x

ggplot(aes(x = difference, y = MeasuredQ_Ls), data = French1comb.2022) +
  geom_point(aes(color = Method), size = 3) +
  geom_smooth(method = "lm", se=FALSE, formula = frch.formula) +
  stat_poly_eq(formula = frch.formula,
               aes(label = paste(..eq.label.., ..rr.label.., sep = "~~~")),
               parse = TRUE) +
  theme_light() +
  ggtitle("French1 all measured Q")

```

Lets try seperate rating curves by method.

```{r, message = FALSE, warning = FALSE}
# rating curve # 
frch.formula <- y ~ x

ggplot(aes(x = difference, y = MeasuredQ_Ls), data = French1comb.2022) +
  geom_point(aes(color = Method), size = 3) +
  geom_smooth(method = "lm", se=FALSE, formula = frch.formula) +
  stat_poly_eq(formula = frch.formula,
               aes(label = paste(..eq.label.., ..rr.label.., sep = "~~~")),
               parse = TRUE) +
  #xlim(216, 216.4) +
  #ylim(0,1500) +
  theme_light() +
  ggtitle("French all measured Q") + facet_wrap(~Method)

```

Not good. How about a rating curve just with the wading rod measurements and the 3 low YSI points?

```{r, message = FALSE, warning = FALSE}
French1comb.2022.2 <- French1comb.2022 %>% filter(MeasuredQ_Ls < 430)
# rating curve # 
frch.formula <- y ~ x

ggplot(aes(x = difference, y = MeasuredQ_Ls), data = French1comb.2022.2) +
  geom_point(aes(color = Method), size = 3) +
  geom_smooth(method = "lm", se=FALSE, formula = frch.formula) +
  stat_poly_eq(formula = frch.formula,
               aes(label = paste(..eq.label.., ..rr.label.., sep = "~~~")),
               parse = TRUE) +
  #xlim(216, 216.4) +
  #ylim(0,1500) +
  theme_light() +
  ggtitle("French measured Q")

```

Not good at low Q, but lets add back in the two high difference YSI points.

```{r, message = FALSE, warning = FALSE}
French1comb.2022.3 <- French1comb.2022 %>% filter(MeasuredQ_Ls < 430 | difference > 10)
# rating curve # 
frch.formula <- y ~ x

ggplot(aes(x = difference, y = MeasuredQ_Ls), data = French1comb.2022.3) +
  geom_point(aes(color = Method), size = 3) +
  geom_smooth(method = "lm", se=FALSE, formula = frch.formula) +
  stat_poly_eq(formula = frch.formula,
               aes(label = paste(..eq.label.., ..rr.label.., sep = "~~~")),
               parse = TRUE) +
  #xlim(216, 216.4) +
  #ylim(0,1500) +
  theme_light() +
  ggtitle("French measured Q")

```


```{r, message = FALSE, warning = FALSE}
## Predict STRT Q
FRCH.lm.2022 <- lm(French1comb.2022.3$MeasuredQ_Ls ~ French1comb.2022.3$difference)
summary(FRCH.lm.2022)

FRCH.2022.dt$pred.frch.Q <- coef(FRCH.lm.2022)[2] * FRCH.2022.dt$difference + coef(FRCH.lm.2022)[1]

FRCH.2022.dt <- FRCH.2022.dt %>% filter(!pred.frch.Q %in% NA)

FRCH.2022.dt %>% ggplot(aes(x = DateTimeAK, y = pred.frch.Q)) +
  geom_line(color="#A6CEE3", size=1.25) +
  geom_point(data = French1comb.2022, aes(x = DateTimeAK, y = MeasuredQ_Ls, color = Method), size=3) +
  theme_classic() +
  ggtitle("FRCH predicted and measured Q") +
  xlab("Date") +
  ylab("Discharge (L/s)")

```
This doesn't fit well at low Q especially.



### VAUL ###

```{r, message = FALSE, warning = FALSE}
vaul.stream.one.2022.url <- "https://docs.google.com/spreadsheets/d/e/2PACX-1vQf78OhtBtjvs6HmnEVPJ0PVYSlpIjVAom5VIv12LhZDMbezaFb-LJCGMZUoyVjLJI-pqizM-Be2hbl/pubhtml"
vaul.stream.two.2022.url <- "https://docs.google.com/spreadsheets/d/e/2PACX-1vSR7qqdF5BXklT1ocG9bLLUwJ07ha8qmzAVRPaUjm7mUq12VptmViI9NJcW1-jO4cu0KtHBLl90A4DZ/pub?output=csv"

# load in url
vaul.stream.one.2022 <- read.csv(url(vaul.stream.one.2022.url), skip = 1) 
vaul.stream.two.2022 <- read.csv(url(vaul.stream.two.2022.url), skip = 1) 

# clean for merging purposes
vaul.stream.one.2022 <- vaul.stream.one.2022[, -c(5:13)] # removing columns that arent date/abs pressure and temp

vaul.stream.two.2022 <- vaul.stream.two.2022[, -c(5:13)] # removing columns that arent date/abs pressure and temp

# changing to AK time (It reads in as GMT but it is actually AKST )

vaul.stream.two.2022$DateTimeAK <- mdy_hms(vaul.stream.two.2022$Date.Time..GMT.08.00)

vaul.stream.two.2022$DateTimeAK <- force_tz(vaul.stream.two.2022$DateTimeAK, "America/Anchorage")

#vaul.stream.one.2022$DateTimeAK <- mdy_hms(vaul.stream.one.2022$Date.Time..GMT.08.00)

#vaul.stream.one.2022$DateTimeAK <- force_tz(vaul.stream.one.2022$DateTimeAK, "America/Anchorage")


# round date to 5 minute intervals
#vaul.stream.one.2022$DateTimeAK <- lubridate::round_date(vaul.stream.one.2022$DateTimeAK, "5 minutes")
vaul.stream.two.2022$DateTimeAK <- lubridate::round_date(vaul.stream.two.2022$DateTimeAK, "5 minutes")

# cleaning off original datetime 
#vaul.stream.one.2022 <- vaul.stream.one.2022[, -c(2)] # removing columns that aren't date/abs pressure and temp
vaul.stream.two.2022 <- vaul.stream.two.2022[, -c(2)] # removing columns that arent 

#names(vaul.stream.one.2022) <- c("Site", "WaterPressure", "TempC", "DateTimeAK")

names(vaul.stream.two.2022) <- c("Site", "WaterPressure", "TempC", "DateTimeAK")

ggplot(vaul.stream.two.2022, aes(x = DateTimeAK, y = WaterPressure))+
  geom_point() +
  theme_classic()

```

This is the raw record of VAUL pressure. The beginning is airpressure and then there is a gap as we had a relaunch issue. 

```{r, message = FALSE, warning = FALSE}
vaul.stream.two.2022 <- vaul.stream.two.2022 %>%
  mutate(across(c(WaterPressure), 
                ~ifelse(DateTimeAK <= "2022-05-26", NA, .))) # PT wasnt placed into the stream until 5/26

vaul.stream.two.2022 <- vaul.stream.two.2022 %>%
  mutate(across(c(WaterPressure), 
                ~ifelse(DateTimeAK >= "2022-08-15" & DateTimeAK <= "2022-08-31" &
  WaterPressure < 98, NA, .)))

vaul.stream.two.2022 <- vaul.stream.two.2022 %>%
  mutate(across(c(WaterPressure), 
                ~ifelse(DateTimeAK >= "2022-09-20" & DateTimeAK <= "2022-10-01" &
  WaterPressure < 98, NA, .)))

vaul.stream.two.2022 <- vaul.stream.two.2022 %>%
  mutate(across(c(WaterPressure), 
                ~ifelse(DateTimeAK >= "2022-10-10" &
  WaterPressure < 99, NA, .)))

# Clear up strange messiness on 10/11
vaul.stream.two.2022 <- vaul.stream.two.2022 %>%
  mutate(across(c(WaterPressure), 
                ~ifelse(DateTimeAK > "2022-10-11 13:55:00" & DateTimeAK < "2022-10-11 19:10:00", NA, .)))
a <- vaul.stream.two.2022 %>% filter(DateTimeAK == "2022-10-11 13:55:00")
b<- vaul.stream.two.2022 %>% filter(DateTimeAK == "2022-10-11 19:10:00")
a$WaterPressure-b$WaterPressure # 0.924

vaul.stream.two.2022 <- vaul.stream.two.2022 %>%
  mutate(across(c(WaterPressure), 
                ~ifelse(DateTimeAK < "2022-10-11 19:10:00", WaterPressure, WaterPressure + 0.924)))

vaul.stream.two.2022 %>% 
  #filter(DateTimeAK > "2022-10-10") %>% 
  ggplot( aes(x = DateTimeAK, y = WaterPressure))+
  geom_point() +
  theme_classic()

```

That is better. Crazy how fast the water level comes down at VAUL

```{r, message = FALSE, warning = FALSE}
# Join the atmospheric and water pressure together
vaul.final.pressure.2022 <- vaul.stream.two.2022
# Eielson atmosphere data
VAUL.2022 <- left_join(eielson.atmo.2022.compare, vaul.final.pressure.2022 , by = "DateTimeAK")

# Water pressure - atmospheric pressure 
VAUL.2022$difference <- VAUL.2022$WaterPressure - VAUL.2022$AirPressureCorrectedVAUL

VAUL.2022 <-  VAUL.2022[ , -which(names(VAUL.2022) %in% c("TempC"))] # removing columns I do not need

VAUL.2022$Site <- "VAUL"

# Plot air and water pressure
VAUL.2022 %>% filter(DateTimeAK > "2022-05-15") %>% 
  ggplot(aes(DateTimeAK, WaterPressure)) + geom_point() + geom_point(aes(DateTimeAK, AirPressureCorrectedVAUL), color = "red") +
  ggtitle("VAUL air and water pressure")
```


```{r, message = FALSE, warning = FALSE}
vaul.final.pressure.2022.2 <- vaul.final.pressure.2022

VAUL.2022.2 <- left_join(eielson.atmo.2022.compare, vaul.final.pressure.2022.2, by = "DateTimeAK") %>% filter(DateTimeAK > "2022-05-24")

# Water pressure - atmospheric pressure 
VAUL.2022.2$difference <- VAUL.2022.2$WaterPressure - VAUL.2022.2$AirPressureCorrectedVAUL


# Plot difference
VAUL.2022.2 %>% ggplot(aes(DateTimeAK, difference)) + geom_point() + ggtitle("VAUL difference")
```


```{r, message = FALSE, warning = FALSE}
### Filter VAUL ###
# Remove measurements during pressure gap!
QSummary.VA.2022 <- QSummary.2022 %>% filter(Site =="VAUL") %>% filter(DateTimeAK < "2022-06-07" | DateTimeAK > "2022-08-01")

ggplot(QSummary.VA.2022) +
  geom_point(aes(x = DateTimeAK, y = MeasuredQ_Ls, shape = Method, color = Site), size=3) +
  theme_classic() +
  scale_color_manual(values=c("#E7298A")) + 
  ggtitle("VAUL") 

```


```{r, message = FALSE, warning = FALSE}
# Merge by nearest date if we have an offset point 
VAUL.2022.dt <- setDT(VAUL.2022.2) %>% filter(!WaterPressure %in% NA)
QSummary.VA.2022.dt <- QSummary.VA.2022 %>% filter(DateTimeAK > "2022-05-25" & DateTimeAK < "2022-10-01")

Vault1comb.2022 <- VAUL.2022.dt[QSummary.VA.2022.dt, on = "DateTimeAK", roll = 'nearest']
```

```{r}
# rating curve # 
vaul.formula <- y ~ x

Vault1comb.2022  %>% ggplot(aes(x = difference, y = MeasuredQ_Ls)) +
  geom_point(aes(color = Method), size = 3) +
  geom_smooth(method = "lm", se=FALSE, formula = vaul.formula) +
  stat_poly_eq(formula = vaul.formula,
               aes(label = paste(..eq.label.., ..rr.label.., sep = "~~~")),
               parse = TRUE) +
  theme_light() +
  ggtitle("Vault all measured Q")
```

That very high difference could be accurate, but necessary to remove for curve. Let's also remove the two low difference, high Q points.

```{r}
# Remove high difference point
Vault1comb.2022.2 <- Vault1comb.2022 %>% filter(MeasuredQ_Ls < 200)

# rating curve # 
vaul.formula <- y ~ x

Vault1comb.2022.2  %>% ggplot(aes(x = difference, y = MeasuredQ_Ls)) +
  geom_point(aes(color = Method), size = 3) +
  geom_smooth(method = "lm", se=FALSE, formula = vaul.formula) +
  stat_poly_eq(formula = vaul.formula,
               aes(label = paste(..eq.label.., ..rr.label.., sep = "~~~")),
               parse = TRUE) +
  theme_light() +
  ggtitle("Vault measured Q")

```

Let's try curve with wading rod and YSI averaged by date.

```{r}
Vault1comb.2022.3 <- Vault1comb.2022.2 %>% group_by(Date) %>% summarise(MeasuredQ_Ls = mean(MeasuredQ_Ls),
difference = mean(difference))

# rating curve # 
vaul.formula <- y ~ x

Vault1comb.2022.3 %>% filter(MeasuredQ_Ls < 150) %>% ggplot(aes(x = difference, y = MeasuredQ_Ls)) +
  geom_point(size = 3) +
  geom_smooth(method = "lm", se=FALSE, formula = vaul.formula) +
  stat_poly_eq(formula = vaul.formula,
               aes(label = paste(..eq.label.., ..rr.label.., sep = "~~~")),
               parse = TRUE) +
  theme_light() +
  ggtitle("Vault measured Q averaged by date")
```

Let's try separate curves for YSI and wading rod

```{r}

# rating curve # 
vaul.formula <- y ~ x

Vault1comb.2022.2  %>% ggplot(aes(x = difference, y = MeasuredQ_Ls)) +
  geom_point(aes(color = Method), size = 3) +
  geom_smooth(method = "lm", se=FALSE, formula = vaul.formula) +
  stat_poly_eq(formula = vaul.formula,
               aes(label = paste(..eq.label.., ..rr.label.., sep = "~~~")),
               parse = TRUE) +
  #xlim(216, 216.4) +
  #ylim(0,1500) +
  theme_light() +
  ggtitle("Vault measured Q by method") + facet_wrap(~Method)
```

Maybe the best we can do is using the wading rod points with a couple low YSI points.

```{r}
# Remove high difference point
Vault1comb.2022.3 <- Vault1comb.2022 %>% filter(MeasuredQ_Ls < 130)

# rating curve # 
vaul.formula <- y ~ x

Vault1comb.2022.3  %>% ggplot(aes(x = difference, y = MeasuredQ_Ls)) +
  geom_point(aes(color = Method), size = 3) +
  geom_smooth(method = "lm", se=FALSE, formula = vaul.formula) +
  stat_poly_eq(formula = vaul.formula,
               aes(label = paste(..eq.label.., ..rr.label.., sep = "~~~")),
               parse = TRUE) +
  theme_light() +
  ggtitle("Vault measured Q")

```

```{r, message = FALSE, warning = FALSE}
## Predict VAUL Q
VAUL.lm.2022 <- lm(Vault1comb.2022.3$MeasuredQ_Ls ~ Vault1comb.2022.3$difference)
summary(VAUL.lm.2022)

VAUL.2022.dt$pred.vaul.Q <- coef(VAUL.lm.2022)[2] * VAUL.2022.dt$difference + coef(VAUL.lm.2022)[1]

VAUL.2022.dt <- VAUL.2022.dt %>% select(DateTimeAK, pred.vaul.Q) %>% na.omit()

VAUL.2022.dt %>% ggplot(aes(x = DateTimeAK, y = pred.vaul.Q)) +
  geom_line(color="#A6CEE3", size=1.25) +
  geom_point(data = Vault1comb.2022, aes(x = DateTimeAK, y = MeasuredQ_Ls, color = Method), size=3) +
  theme_classic() +
  ggtitle("VAUL predicted and measured Q") +
  xlab("Date") +
  ylab("Discharge (L/s)")

```


### Export 2022 predicted Q
```{r}
names(FRCH.2022.dt)
pred_Q.1 <- full_join(VAUL.2022.dt, MOOS.2022.dt)
pred_Q.2 <- full_join(pred_Q.1, POKE.2022.dt)
pred_Q.3 <- full_join(STRT.2022.dt[,c(1,10)], FRCH.2022.dt[,c(1,12)])
pred_Q_2022 <- full_join(pred_Q.2, pred_Q.3)

names(pred_Q_2022) <- c("DateTimeAK", "pred.vaul.Q", "pred.moos.Q", "pred.poke.Q", "pred.strt.Q", "pred.frch.Q")
write.csv(pred_Q_2022, "Predicted_Q_2022.csv")
pred_Q_2022 %>% ggplot() + geom_line(aes(DateTimeAK, pred.vaul.Q), col = 1)+ geom_line(aes(DateTimeAK, pred.moos.Q), col = 2)+ geom_line(aes(DateTimeAK, pred.poke.Q), col = 3)+ geom_line(aes(DateTimeAK, pred.strt.Q), col = 4)+ geom_line(aes(DateTimeAK, pred.frch.Q), col = 5) + ylab("Predicted Q")
```